article title

### 2022-07-19 article.tex
Add Greek unicode letters

>>>>

\subsection{Greek unicode}
\label{sec:greek_unicode}

Greek letters can be inserted in mathematics and text using Unicode characters. In Neovim, the sequence is `ControlKey + v uhhhh` where `hhhh` is the Unicode.

alpha 03b1 α 0391 Α \\
beta 03b2 β 0392 Β \\
gamma 03b3 γ 0393 Γ \\
delta 03b4 δ 0394 Δ \\
epsilon 03b5 ε 0395 Ε \\
zeta 03b6 ζ 0396 Ζ \\
eta 03b7 η 0397 Η \\
theta 03b8 θ 0398 Θ \\
iota 03b9 ι 0399 Ι \\
kappa 03b1 α 039a Κ \\
lambda 03bb λ 039b Λ \\
mu 03bc μ 039c Μ \\
nu 03bd ν 039d Ν \\
xi 03be ξ 039e Ξ \\
omicron o O \\
pi 03c0 π 03ao Π \\
rho 03c1 ρ 03a1 Ρ \\
sigma 03c3 σ 03a3 Σ \\
tau 03c4 τ 03a4 Τ \\
upsilon 03c5 υ 03a5 Υ \\
phi 03c6 φ 03a6 Φ \\
chi 03c7 χ 03a7 Χ \\
psi 03c8 ψ 03a8 Ψ \\
omega 03c9 ω 03a9 Ω \\
